DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-10 paper/core/exp_setup.tex
separate repo for network
added results chart and table

The training takes around $1.5$ hours on \emph{Nvidia GTX} $1070$ and around $15$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance.

>>>>

The training takes around $35$ minutes on \emph{Nvidia GTX} $1070$ and around $12$ hours on \emph{Nvidia GTX} $840m$, which is a relatively small time based on both \emph{GPUs} performance. \\

The proposed network is implemented in \emph{Python} using \emph{PyTorch} framework \cite{paszke2019pytorch}.  Our source code is publicly available at \link{https://github.com/DarkGeekMS/deepsched}.
